\section*{Introduction}
\addcontentsline{toc}{section}{Introduction}
In this article, I am introducing sheaf theory and sheaf cohomology
in the context of algebraic geometry to prove the Riemann-Roch theorem,
which is one of the most important theorems in the classification
of algebraic curves. This text is aimed at undergraduate students with
basic knowledge of varieties.

Sheaves are a way of associating algebraic data to a space locally. We
usually associate data consisting of rational functions, and the
Riemann-Roch theorem will give global information about certain types of
functions on a space. In this article, I will use the Riemann-Roch theorem
to show the existance of a globally defined function on a curve $X$ of genus
0 that defines an isomorphism with the projective line. Thus, we get a
complete classification of curves of genus 0. One can use the Riemann-Roch
theorem to classify curves of higher genera as well.

The main ingredient in the proof of the Riemann-Roch theorem is Serre
duality, which is a more general result. The proof will again
be cohomological and is usually rather abstract. However, I will
approach the proof by giving concrete interpretations of
the cohomology groups by following Serre's exposition in \cite{serre}.

The reader is assumed to be know basic algebraic geometry. An excellent
introduction to the topic is \cite{reid}, and a good set of lecture notes
which goes beyond the basics is \cite{gathmann}. I will use the language
of discrete valuation rings, which is not explained in this paper. See
\cite{fulton} for an introduction to this topic. Familiarity with the basic
constructions of homological algebra is helpful if not necessary. Through
out the paper, I will also try to point out category theoretical contexts of
the concepts discussed. However, it is not necessary to know any category
theory to understand this paper, and I will always place a warning for
people who are not fond of abstract nonsense.
