\section{Sheaves}
The central objects of study in this paper are \emph{sheaves}. I will begin
this section by motivating sheaves by looking at \emph{fibre bundles},
which show up through out geometry and topology.

\begin{cat}
  Suppose $\mathcal{F}: \text{Op}(X)^{\text{op}}\to\mathcal{C}$ is a pre-sheaf.
  If $\mathcal{C}$ has limits, we can express the sheaf axioms in the
  language of equalisers. Namely, $\mathcal{F}$ is a sheaf if for every
  open set $U$ of $X$ and an open cover $U_{i}$ of $U$ the following
  diagram is an equaliser diagram.
  \begin{equation}\label{diag:sheaf_eq}\begin{tikzcd}
      \mathcal{F}(U)\rar
      & \displaystyle\prod_{i}\mathcal{F}(U_{i})\rar[shift left]\rar[shift right]
      & \displaystyle\prod_{i,j}\mathcal{F}(U_{i}\cap U_{j})
    \end{tikzcd},\end{equation}
  where the first map is the product of the restrictions
  $\text{res}_{U}^{U_{i}}$ and the pair of maps are products of the
  restrictions $\text{res}_{U_{i}}^{U_{i}\cap U_{j}}$ and
  $\text{res}_{U_{j}}^{U_{i}\cap U_{j}}$ respectively.
\end{cat}

The category of sheaves which takes values in an abelian category is
itself abelian, so we can do homological algebra in it.
\begin{cat}
  Equaliser diagrams in abelian categories can be expressed in terms
  of exact sequences. Therefore, the diagram \eqref{diag:sheaf_eq}
  can be expressed as the exact sequence
  \begin{equation}\label{diag:sheaf_ex}\begin{tikzcd}
      0\rar & \mathcal{F}(U)\rar & \displaystyle\prod_{i}\mathcal{F}(U_{i})
      \rar{\text{res}_{U_{i}}^{U_{i}\cap U_{j}}-\text{res}_{U_{j}}^{U_{i}\cap U_{j}}}
      &[5em] \displaystyle\prod_{i,j}\mathcal{F}(U_{i}\cap U_{j})
    \end{tikzcd},\end{equation}
  when the sheaf takes values in an abelian category.
\end{cat}

\begin{thm}\label{thm:ses_equivalence}
  For a collection $(\mathscr{F}_{i})_{i\in\mathbb{Z}}$ of sheaves on
  a variety $X$ and maps ${\mathscr{F}_{i}\to\mathscr{F}_{i+1}}$,
  the following are equivalent.
  \begin{enumerate}[(i)]
    \item The sequence
          \[
          \begin{tikzcd}
            \cdots \rar & \mathscr{F}_{i-1}\rar
            & \mathscr{F}_{i}\rar & \mathscr{F}_{i+1}\rar & \cdots
          \end{tikzcd}
          \]
          is exact.
    \item There is an open cover $(U_{j})_{j\in\mathbb{I}}$ of $X$ such that
          the sequence
          \[
          \begin{tikzcd}
            \cdots \rar & \mathscr{F}_{i-1}\mid_{U_{j}}\rar
            & \mathscr{F}_{i}\mid_{U_{j}}\rar
            & \mathscr{F}_{i+1}\mid_{U_{j}}\rar & \cdots
          \end{tikzcd}
          \]
          is exact for every $j\in I$.
    \item For every $P\in X$, the induced sequence
          \[
          \begin{tikzcd}
            \cdots \rar & (\mathscr{F}_{i-1})_{P}\rar
            & (\mathscr{F}_{i})_{P}\rar
            & (\mathscr{F}_{i+1})_{P}\rar & \cdots
          \end{tikzcd}
          \]
          is exact.
  \end{enumerate}
\end{thm}
